---
title: "P8105 HW5"
author: "Kehan Su"
date: "2024-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
```

## Problem 1

```{r}
bday_sim = function(n) {
  
  bdays = sample(1:365, size = n, replace = TRUE)
  
  duplicate = length(unique(bdays)) < n
  
  return(duplicate)
}
```

```{r}
sim_res = 
  expand_grid(
    n = c(2:50),
    iter = 1:10000
  ) |>
  mutate(res = map_lgl(n,bday_sim)) |>
  group_by(n) |>
  summarize(prob = mean(res))

sim_res |>
  ggplot(aes(x = n, y = prob)) +
  geom_line() 
```

## Problem 2

```{r}
# Function to simulate the experiment
exp_sim = function(mu) {
  data = rnorm(30, mean = mu, sd = 5)
  tidy_result = 
    broom::tidy(t.test(data, mu = 0)) |>
    select(estimate, p.value)
  return(tidy_result)
}

# Simulate experiments for different mu values
exp_df = 
  expand.grid(
    mu = c(0:6),
    iter = 1:5000
  ) |>
  mutate(result = map(mu, exp_sim)) |>
  unnest(result)
```

```{r}
# Calculate power and mean estimates
exp_df_summary = exp_df |>
  group_by(mu) |>
  summarise(
    power = sum(p.value < 0.05),
    mean_estimate_all = mean(estimate),
    mean_estimate_reject = mean(estimate[p.value < 0.05])
  )

# Convert power to a proportion
exp_df_summary$power <- exp_df_summary$power / 5000

# Plot 1: Power vs Effect Size
ggplot(exp_df_summary, aes(x = mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(x = "True value of Î¼", y = "Power", title = "Power of the Test by Effect Size") +
  geom_hline(yintercept = 0.05, linetype = "dashed", color = "red")
```
The plot shows a positive association between effect size (true value of mu) and the power of the test.

```{r}
# Plot 2: Average Estimate of Î¼ vs True Value of Î¼
ggplot(exp_df_summary, aes(x = mu)) +
  geom_line(aes(y = mean_estimate_all, color = "All Data")) +
  geom_point(aes(y = mean_estimate_all, color = "All Data")) +
  geom_line(aes(y = mean_estimate_reject, color = "Rejected Data")) +
  geom_point(aes(y = mean_estimate_reject, color = "Rejected Data")) +
  scale_color_manual(name = "Data Type", values = c("All Data" = "blue", "Rejected Data" = "red")) +
  labs(x = "True value of Î¼", y = "Average Estimate of Î¼", title = "Average Estimate of Î¼ by True Value of Î¼") +
  theme_minimal() +
  theme(legend.position = "right")
```
The sample average of ðœ‡Ì‚ across tests for which the null is rejecte dis not approximately equal to the true value of ðœ‡. It is because of selection bias. When filtering only for tests where the null hypothesis was rejected, we tend to get samples where random variation pushed the sample mean further from zero, which increases the likelihood of rejecting the null.


## Problem 3

```{r}
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data = read_csv(url)
```
```{r}
# Summarize the data
summarized_data = homicide_data |>
    mutate(city_state = paste(city, state, sep = ","),
    unsolved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), 1, 0)
    ) |>
  filter(!(city_state == "Tulsa,AL")) |>
  group_by(city_state) |>
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(unsolved)
  )
```

```{r}
# Test for Baltimore
baltimore_data =
  summarized_data |>
  filter(city_state == "Baltimore,MD")

baltimore_prop_test = baltimore_data |>
  with(prop.test(unsolved_homicides, total_homicides))

baltimore_summary = 
  broom::tidy(baltimore_prop_test) |>
  select(estimate, conf.low, conf.high)

baltimore_summary
```
```{r}
# Test for all cities
city_results = summarized_data |>
  mutate(
    test_result = purrr::map2(unsolved_homicides, total_homicides, ~ prop.test(.x, .y) |> broom::tidy())
  ) |>
  unnest(test_result) |>
  select(city_state, estimate, conf.low, conf.high)
city_results
```
```{r}
city_results |>
  mutate(city_state = fct_reorder(city_state, estimate)) |>
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  coord_flip() +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Proportion of Unsolved Homicides"
  )
```
